\documentclass[10pt]{article}
\usepackage{graphicx}

\usepackage{longtable}
\usepackage{array}


\newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{0.25\textwidth}|}


%------------------------------------------------------------
%	TITLE
%------------------------------------------------------------
\title{Forecasting Macroeconomic Parameters with Deep Learning Neural Networks \\ Project Reading List}
\date{\today}
\author{Stefan Kokov}


%------------------------------------------------------------
%	BEGIN DOCUMENT
%------------------------------------------------------------
\begin{document}


%------------------------------------------------------------
%	MAKE TITLE
%------------------------------------------------------------
\maketitle


%------------------------------------------------------------
%	BOOKS
%------------------------------------------------------------
\section{Books}
\begin{itemize}
	\item Deep Learning \cite{goodfellow_bengio_courville_2017} - reading chapters on convolutional neural networks and recurrent neural networks.
\end{itemize}


%------------------------------------------------------------
%	PROJECTS
%------------------------------------------------------------
\section{Past Projects}
\begin{itemize}
	\item Forecasting Macroeconomic Data with Neural Networks \cite{bassi}.
	\item Equation Discovery for Macroeconomic Modelling: an Ordinary Differential Equations appoach \cite{Georgiev}.
\end{itemize}


%------------------------------------------------------------
%	PAPERS
%------------------------------------------------------------
\section{Papers}
\begin{center}

	\begin{longtable}{ | P | P | P | P |}
  
    \hline
    Paper & Application & Results & Key Concepts \\ \hline
    %------------------------------------------------------------
    %	ROW 1
    %------------------------------------------------------------
    Introduction to financial forecasting \cite{Abu-Mostafa1996}
	& 
	Neural networks for financial forecasting with a focus on commodity futures and foreign exchange. 
	&
	Custom features derived using domain knowledge ("hints"), achieved good accuracy of their algorithm. 
	& 
    Input feature selection. \linebreak Problems arraising from the noisy nature of financial data. 
    \\  \hline
    %------------------------------------------------------------
    %	ROW 2
    %------------------------------------------------------------ 
	Equation Discovery for Macroeconomic Modelling  \cite{dimitar}  
    &
    Using LAGRAMGE equation discovery tool to find macroeconomic models, which both minimise error in predictions and provide a theoretical insight. 
    &
    Several models which achieve good predictions are found. They are not based on iterative re-estimation, which might mean they are theoritically sound.
    &
    Equation Discovery 
    \linebreak
    Macroeconomic parameters used: inflation, output, interest rate
    \linebreak
    Macroeconomic background - empirical modelling of the inflation process.
   	\\  \hline
   	
   	%------------------------------------------------------------
    %	ROW 3
    %------------------------------------------------------------ 
	Forecasting Stock Prices from the Limit Order
Book using Convolutional Neural Networks  \cite{Tsantekidis}  
    &
    Convolutional Neural Network algorithm for predicting stock prices.
    &
    CNN outperforms MLP and SVM.
    &
    Convolutional neural network applied to financial time series data.
    Further work suggestions.
   	\\  \hline
   	
   	%------------------------------------------------------------
    %	ROW 4
    %------------------------------------------------------------ 
	FForecasting with artificial neural networks:: The state of the art  \cite{ZHANG1998}  
    &
    Survey of research in forecasting using neural networks.
    &
    Summurises main aproaches for forecasting using neural networks at the time. Lists the main challenges and compares NN based aproaches to conventional methods.
    &
    Feedforward neural networks for forecasting. \linebreak
    Main characteristics and challanges of using NN.
   	\\  \hline

  	\end{longtable}
\end{center}


%------------------------------------------------------------
%	REFERENCES
%------------------------------------------------------------
\bibliographystyle{ieeetr}
\bibliography{reference} 


\end{document}